---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# curry

`curry` is yet another attempt at providing a native currying mechanism in R. 
Other examples of implementations of function composition can be found in 
[`purrr`](https://CRAN.R-project.org/package=purrr) and 
[`functional`](https://CRAN.R-project.org/package=functional) (and probably 
others). `curry` sets itself apart in the manner it is used and in the functions
it creates. `curry` uses the `%<%` operator to perform currying and a curried
function retains named arguments for easier autocomplete.

## Example

```{r}
library(curry)

list_with_5 <- list %<% 5
list_with_5(10)

chained_curry <- pmin %<% sample(10) %<% sample(10)
chained_curry()
chained_curry(1:10)
```

## Installation
`curry` is still a work in progress but can be installed through devtools:

```r
if (!require(devtools)) {
    install.packages(devtools)
}
devtools::install_github('thomasp85/curry')
```

