---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(curry)
```

# curry

[![Travis-CI Build Status](https://travis-ci.org/thomasp85/curry.svg?branch=master)](https://travis-ci.org/thomasp85/curry)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/thomasp85/curry?branch=master&svg=true)](https://ci.appveyor.com/project/thomasp85/curry)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/curry)](https://cran.r-project.org/package=curry)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/grand-total/curry)](http://cran.r-project.org/package=curry)

`curry` is yet another attempt at providing a native currying/partial 
application mechanism in R. Other examples of implementations of this can be 
found in [`purrr`](https://CRAN.R-project.org/package=purrr) and 
[`functional`](https://CRAN.R-project.org/package=functional) (and probably 
others). `curry` sets itself apart in the manner it is used and in the functions
it creates. `curry` is operator based and a partially applied function retains 
named arguments for easier autocomplete etc. `curry` provides three mechanisms
for partial application: `%<%` (`curry()`), `%-<%` (`tail_curry()`), and `%><%` 
(`partial()`) - see the examples for the differences

## Example

Currying is the reduction of the arity of a function by fixing the first 
argument, returning a new function lacking this.

```{r}
# Equivalent to curry(`+`, 5)
add_5 <- `+` %<% 5
add_5(10)

# ellipsis are retained when currying
bind_5 <- cbind %<% 5
bind_5(1:10)
```

Tail currying is just like currying except it reduces the arity of the function
from the other end by fixing the last argument.

```{r}
# Equivalent to tail_curry(`/`, 5)
divide_by_5 <- `/` %-<% 5
divide_by_5(10)

no_factors <- data.frame %-<% FALSE
df <- no_factors(x = letters[1:5])
class(df$x)
```

When the argument you wish to fix is not in either end of the argument list it
is necessary to use a more generalised approach. Using `%><%` (or `partial()`)
it is possible to fix any (and multiple) arguments in a function using a list of
values to fix.

```{r}
dummy_lengths <- vapply %><% list(FUN = length, FUN.VALUE = integer(1))
test_list <- list(a = 1:5, b = 1:10)
dummy_lengths(test_list)
```

Other efforts in this has the drawback of returning a new function with just an
ellipsis, making argument checks and autocomplete impossible. With `curry` the
returned functions retains named arguments (minus the fixed ones).

```{r}
args(no_factors)
args(dummy_lengths)
```

## Installation
`curry` is still a work in progress but can be installed through devtools:

```r
if (!require(devtools)) {
    install.packages(devtools)
}
devtools::install_github('thomasp85/curry')
```

