---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(curry)
Sys.setenv(LANG = "en")
```

# curry

[![Travis-CI Build Status](https://travis-ci.org/thomasp85/curry.svg?branch=master)](https://travis-ci.org/thomasp85/curry)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/thomasp85/curry?branch=master&svg=true)](https://ci.appveyor.com/project/thomasp85/curry)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/curry)](https://CRAN.R-project.org/package=curry)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/grand-total/curry)](https://CRAN.R-project.org/package=curry)

`curry` is yet another attempt at providing a native currying/partial 
application mechanism in R. Other examples of implementations of this can be 
found in [`purrr`](https://CRAN.R-project.org/package=purrr) and 
[`functional`](https://CRAN.R-project.org/package=functional) (and probably 
others). `curry` sets itself apart in the manner it is used and in the functions
it creates. `curry` is operator based and a partially applied function retains 
named arguments for easier autocomplete etc. `curry` provides three mechanisms
for partial application: `%<%` (`curry()`), `%-<%` (`tail_curry()`), and `%><%` 
(`partial()`) - see the examples for the differences

## Example

### Currying
Currying is the reduction of the arity of a function by fixing the first 
argument, returning a new function lacking this.

```{r}
# Equivalent to curry(`+`, 5)
add_5 <- `+` %<% 5
add_5(10)

# ellipsis are retained when currying
bind_5 <- cbind %<% 5
bind_5(1:10)
```

### Tail currying
Tail currying is just like currying except it reduces the arity of the function
from the other end by fixing the last argument.

```{r}
# Equivalent to tail_curry(`/`, 5)
divide_by_5 <- `/` %-<% 5
divide_by_5(10)

no_factors <- data.frame %-<% FALSE
df <- no_factors(x = letters[1:5])
class(df$x)
```

### Partial function application
When the argument you wish to fix is not in either end of the argument list it
is necessary to use a more generalised approach. Using `%><%` (or `partial()`)
it is possible to fix any (and multiple) arguments in a function using a list of
values to fix.

```{r}
dummy_lengths <- vapply %><% list(FUN = length, FUN.VALUE = integer(1))
test_list <- list(a = 1:5, b = 1:10)
dummy_lengths(test_list)
```

Other efforts in this has the drawback of returning a new function with just an
ellipsis, making argument checks and autocomplete impossible. With `curry` the
returned functions retains named arguments (minus the fixed ones).

```{r}
args(no_factors)
args(dummy_lengths)
```

### Real currying
The above uses a very loose (incorrect) definition of currying. The correct
definition is that currying a function returns a function taking a single 
argument (the first from the original function). Calling a curried function will
return a new function accepting the second argument of the original function and
so on. Once all arguments of the original function has been consumed it 
evaluates the call and returns the result. Thus:

```{r, eval=FALSE}
# Correct currying
foo(arg1)(arg2)(arg3)

# Incorrect currying
foo(arg1)(arg2, arg3)
```

True currying is less useful in R as it does not play nice with function 
containing `...` as the argument list will never be consumed. Still, it is 
available in `curry` using the `Curry()` function or the `%<!%` operator:

```{r}
testfun <- function(x = 10, y, z) {
  x + y + z
}
curriedfun <- Curry(testfun)
curriedfun(1)(2)(3)

# Using the operator
testfun %<!% 1 %<!% 2 %<!% 3

# The strict operator is only required for the first call
testfun %<!% 1 %<% 2 %<% 3
```

As with the partial application functionality the strict currying retains
argument names and defaults at each step of the currying sequence:

```{r}
args(curriedfun)
```

### Weak partial function application
The last functionality provided by `curry` is a *"weak"* partial function 
application in the sense that it sets (or changes) argument defaults. Thus, 
compared to partial application it returns a function with the same arguments,
but if the defaulted arguments are ignored it will be equivalent to a partial
application. Defaults can be set or changed using the `set_defaults()` function
or the `%<?%` operator:

```{r, error = TRUE}
testfun <- function(x = 1, y = 2, z = 3) {
  x + y + z
}
testfun()
testfun2 <- testfun %<?% list(y = 10)
testfun3 <- testfun %><% list(y = 10)
testfun2()
testfun3()

testfun2(y = 20)
testfun3(y = 20)
```


## Installation
`curry` can be installed from CRAN:

```{r, eval=FALSE}
install.packages('curry')
```

or GitHub for the latest version:

```{r, eval=FALSE}
if (!require(devtools)) {
    install.packages(devtools)
}
devtools::install_github('thomasp85/curry')
```
